junk_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

```{r}
url <- "https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/dummy_df.csv"

@@

## Creating a corpus
```{r}
df_corp <- df
df_corp <- df_corp %>% rename(text = Summary)
corp <- corpus(df_corp)

@@

##Creatung a dfm from the corpus
```{r}
dfm_corp <- corp %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

>>>>

```{r}

url <- "data/data_11_28.csv"

@@

## Creating a corpus
```{r}
df_corp <- df
df_corp <- df_corp %>% rename(text = summary)
corp <- corpus(df_corp)

@@

##Creatung a dfm from the corpus
```{r}
dfm_corp <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used"))%>%
  dfm()
